A Formal Model of Checked C

### 2023-01-18 sandp23/evaluation.tex
Adding all

\input{figures/memoryoverhead}
The~\fig{fig:runtimeoverhead} shows the overhead of the partitioned programs.
It is interesting to see a lot of variance in the runtime overhead.
Our analysis shows that the runtime overhead is proportional to the execution time spent in the sandbox and the number of transitions between~\cregion and the sandbox.
This is expected because of the overhead in sandbox execution, as shown by our micro-benchmarks experiments (\fig{fig:microbenchmarks}).
The~\tbl{table:conversioneffort} shows the number of lines in the sandbox for each of the partitioned programs.
For~\texttt{ProFTPD}, we used only tainted pointers with no code in the sandbox, and there were also no transitions to/from the sandbox.
Consequently, the overhead is very less 4.2\%.
For~\texttt{UFTPD} and~\texttt{MicroHTTPD}, we partitioned only request handlers (that are relatively small) into the sandbox. These handlers parse the message and return the actions that need to be performed. The server only invokes these handles on particular requests resulting in less number of transitions into the sandbox. As expected, the overhead is also very less in these cases.
For~\texttt{TinyBigNum} and~\texttt{Parsons}, the overhead is very high because of the relatively large amount of code in sandbox region.
In both these applications, we place the frequently used parsing functions in the sandbox resulting in a lot of sandbox transitions with most of them in a loop.
As expected, the overhead is very high.
The case is slightly different in~\texttt{pnm2png} and~\texttt{png2pnm} where we made the entire~\code{png} structure tainted, which resulted in dynamic checks every time any part of the~\code{png} struct is accessed, resulting in slightly higher overhead.
In summary:
\begin{itemize}
  \item The runtime overhead of the partioned program directly depends on that of the target sandbox.
  \item Run-time Overhead is proportional to the extent of annotated pointers, sandboxed code, and transitions between~\cregion and sandbox.
  \item Tainting heavily used pointers leads to high overhead.
\end{itemize}

>>>>

%\input{figures/memoryoverhead}
The~\fig{fig:runtimeoverhead} shows the overhead of the partitioned programs.
It is interesting to see a lot of variance in the runtime overhead.
Our analysis shows that the runtime overhead is proportional to the execution time spent in the sandbox and the number of transitions between~\cregion and the sandbox.
This is expected because of the overhead in sandbox execution, as shown by our micro-benchmarks experiments (\fig{fig:microbenchmarks}).
The~\tbl{table:conversioneffort} shows the number of lines in the sandbox for each of the partitioned programs.
For~\texttt{ProFTPD}, we used only tainted pointers with no code in the sandbox, and there were also no transitions to/from the sandbox.
Consequently, the overhead is very less 4.2\%.
For~\texttt{UFTPD} and~\texttt{MicroHTTPD}, we partitioned only request handlers (that are relatively small) into the sandbox. These handlers parse the message and return the actions that need to be performed. The server only invokes these handles on particular requests resulting in less number of transitions into the sandbox. As expected, the overhead is also very less in these cases.
For~\texttt{TinyBigNum} and~\texttt{Parsons}, the overhead is very high because of the relatively large amount of code in sandbox region.
In both these applications, we place the frequently used parsing functions in the sandbox resulting in a lot of sandbox transitions with most of them in a loop.
As expected, the overhead is very high.
The case is slightly different in~\texttt{pnm2png} and~\texttt{png2pnm} where we made the entire~\code{png} structure tainted, which resulted in dynamic checks every time any part of the~\code{png} struct is accessed, resulting in slightly higher overhead.
In summary:
\begin{itemize}
  \item The runtime overhead of the partioned program directly depends on that of the target sandbox.
  \item Run-time Overhead is proportional to the extent of annotated pointers, sandboxed code, and transitions between~\cregion and sandbox.
  \item Tainting heavily used pointers leads to high overhead.
\end{itemize}

\subsubsection{Memory Overhead}
All programs have a constant memory overhead ($\sim$81 KB) mainly for sandbox and a few variables related to creating sandbox and other helper functions.
However, similar to the original~\checkedc,~\systemname{} itself doesn't add any memory overhead.
This is expected because, similar to~\checkedc types, ~\code{taint}ed pointers also do not have metadata and have the same runtime representation as regular pointers.
